### 2022-01-10 src-latex/parts/20-related-work.tex
Finished Related Work last section (V1)

Most of the current state-of-the-art OCR systems, like Tesseract \cite{smith2007overview}, OCRopus \cite{breuel2008ocropus} and PERO OCR \cite{kohut2021ts} are based on a pipeline of convolutional neural networks (CNNs) and long short-term memory networks (LSTM). Although this kind of model produces good results on modern texts, it faces several challenges with ancient texts, such as the lack of annotated data for learning, or different transcriptions styles in training data.

\cite{martinek2019hybrid} propose an approach to generate synthetic annotated text for historical OCR training, based on manually collected characters from historical text images. This work propose to train an OCR system based on a CNN-
LSTM network with the synthetic data and then to fine-tune the model with some pages of real historical annotated text. The results show that this approach gives state-of-the-art results.

To overcome the limitations due to different transcription styles in training data, PERO OCR adds a Transcription Style Block layer to a classical model based on a CNN and a Recurrent Neural Network components \cite{kohut2021ts}. This block takes the image of the text and a Transcription Style Identifier as inputs and help the network decide what kind of transcription style to use as output.

@@

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}. Rule based approaches look for portions of text that match patterns based on word characteristics such as their case, whether they are digits or not, their part-of-speech tags, etc. These patterns can be fully handcrafted like in \cite{bell2020automated} or generated by data mining approaches like in \cite{nouvel2011}. Rule based approaches can also combine a set of patterns with a set of dictionaries (gazetteers, author lists, etc.) that help recognizing named entities when an exhaustive lexicon of searched entities is available \cite{mansouri2008,maurel2011}. For example, the CasEN\footnote{\url{https://tln.lifat.univ-tours.fr/version-francaise/ressources/casen}} transducer cascade leverages syntatic-lexical patterns and dictionnaries to recognize Named Entities in French texts. Such kind of approaches achieve very good results when applied to specialized domain corpus - like directories - and when exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify words into one category of named entities or another. In recent years, the latter have grown dramatically, yielding state-of-the art performances and establishing new baselines\cite{li2020}. A recent survey proposed by \cite{li2020} presents deep learning techniques for NER according to the distributed representation(s) they use as input, their context encoder and their tag decoder. It shows that language model embeddings pre-trained using \textit{Transformer} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, can not only be used to replace traditional embeddings as input distributed representations but also be fine-tuned for the NER task with one additional output layer while achieving state-of-the-art performances. The survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performances for use cases with domain-specific texts and few training data.

\subsection{Named Entity Recognition on Historical Texts}

\cite{Labusch2020NamedED} apply a BERT-based NER model on historical texts in German, French and English, produced by OCR. It is an of-the-shelf multilingual BERT-based NER model, pre-trained on more than 2 000 000 pages of OCRed historical texts, in the three languages and fine-tuned with historical texts NER ground truth, also in the three languages. Eventually, a clear decrease in NER performance on OCRised texts is noted. Moreover, the article reports that this decrease is more important for English texts for which the OCR is of poorer quality than for texts in the other two languages.

Recently, several studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective ground-truths. For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE} and \textit{Date}. The performance of the NER model with respect to OCR quality is eventually assessed by calculating the F-measure for each NER class, and each article i.e., each WER value. \cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF. They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version. Finally, they applied each NER model on the progressively degraded versions of the corpora and computed the resulting F-measure. Overall, NER F-mesure drops from 90\% to 50\% when the WER increase from 8\% to 50\%. Besides, all NER models are sensitive to OCR errors, but models based on deep neural networks seem less prone to errors.

Based on the observation that OCR errors necessarily affect the performance of NER approaches applied to historical texts, \cite{huynh2020use} and \cite{marz2021data} have proposed different approaches to reduce their negative impact.

>>>>

Most of the current state-of-the-art OCR systems, like Tesseract \cite{smith2007overview}, OCRopus \cite{breuel2008ocropus} and PERO OCR \cite{kohut2021ts} are based on a pipeline of convolutional neural networks (CNNs) and long short-term memory networks (LSTM). Although this kind of model produces good results with modern texts, it faces several challenges with ancient texts, such as the lack of annotated data for learning, or different transcription styles in training data.

\cite{martinek2019hybrid} propose an approach to generate synthetic annotated text for historical OCR training, based on manually collected characters from historical text images. This work proposes to train an OCR system based on a CNN-
LSTM network with synthetic data and then to fine-tune the model with some pages of real historical annotated text. The results show that this approach gives state-of-the-art results.

To overcome the limitations due to different transcription styles in training data, PERO OCR adds a Transcription Style Block layer to a classical model based on a CNN and a Recurrent Neural Network components \cite{kohut2021ts}. This block takes the image of the text and a Transcription Style Identifier as inputs and helps the network decide what kind of transcription style to use as output.

\textcolor{green}{à compléter/retoucher}

@@

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}. Rule based approaches look for portions of text that match patterns based on word characteristics such as their case, whether they are digits or not, their part-of-speech tags, etc. These patterns can be fully handcrafted like in \cite{bell2020automated} or generated by data mining approaches like in \cite{nouvel2011}. Rule based approaches can also combine a set of patterns with a set of dictionaries (gazetteers, author lists, etc.) that help recognizing named entities when an exhaustive lexicon of searched entities is available \cite{mansouri2008,maurel2011}. For example, the CasEN\footnote{\url{https://tln.lifat.univ-tours.fr/version-francaise/ressources/casen}} transducer cascade leverages syntatic lexical patterns and dictionnaries to recognize Named Entities in French texts. Such kind of approaches achieve very good results when applied to specialized domain corpus - like directories - and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify words into one category of named entities or another. In recent years, the latter have grown dramatically, yielding state-of-the-art performances and establishing new baselines\cite{li2020}. A recent survey proposed by \cite{li2020} presents deep learning techniques for NER according to the distributed representation(s) they use as input, their context encoder and their tag decoder. It shows that language model embeddings pretrained using \textit{Transformer} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, can not only be used to replace traditional embeddings as input distributed representations but also be fine-tuned for the NER task with one additional output layer while achieving state-of-the-art performances. The survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data.

\subsection{Named Entity Recognition in Historical Texts}

\cite{Labusch2020NamedED} applied a BERT-based NER model to historical texts in German, French, and English, produced by OCR. It is off-the-shelf multilingual BERT-based NER model, pretrained on more than 2 000 000 pages of OCRed historical texts in three languages and fine-tuned on historical texts NER ground truth, also in three languages. Eventually, a clear decrease in NER performance on OCRised texts is noted. Moreover, the article reports that this decrease is more important for English texts for which the OCR is of poorer quality than for texts in the other two languages.

Several recent studies have focused on the extent to which the quality of the OCR affects the results produced by a NER model.\cite{van2020assessing} assess the impact of OCR on several NLP downstream tasks, including NER. They worked on a corpus published by a post-OCR correction software company, made of many journal articles with different levels of OCR errors and their respective groundtruths. For each OCRed article, the Word Error Rate (WER) is computed and the English model \textit{en-core-web-lg} provided by Spacy\footnote{\url{https://spacy.io/}} library is used to perform NER on \textit{Person}, \textit{GPE} and \textit{Date}. The performance of the NER model with respect to OCR quality is eventually assessed by calculating the F-measure for each NER class, and each article i.e., each WER value. \cite{hamdi2020assessing} performed a similar but more extensive evaluation on four different NER models: CoreNLP using Conditional Random Fields and three deep neural models, BLSTM-CNN, BLSTM-CRF, and BLSTM-CNN-CRF. They tested them on two well-known NER benchmark corpora: CoNLL-02 and CoNLL-03. They applied four different types of OCR noise to each corpus, with two levels of degradation and computed the WER and Character Error Rate (CER) for each degraded version. Finally, they applied each NER model to the progressively degraded versions of the corpus and computed the resulting F-measure. Overall, NER F-mesure drops from 90\% to 50\% when the WER increase from 8\% to 50\%. Besides, all NER models are sensitive to OCR errors, but models based on deep neural networks seem less prone to errors.

Based on the observation that OCR errors necessarily affect the performance of NER models applied to historical texts, \cite{huynh2020use} and \cite{marz2021data} have proposed different approaches to reduce their negative impact. The former uses a spelling correction tool on several corpora with variable OCR error rates, to assess whether spelling correction has a beneficial impact on NER performance or not. The results showed that as long as OCR errors remain low (CER<2\% and WER<10\%), the F-measure of NER results remains stable. It starts to decrease significantly when OCR errors exceed these thresholds. The latter work focuses on adapting the training data to facilitate the generalisation of an off-the-shelf NER model from modern texts to historical texts. Three different NER models are tested on three historical corpora, in French, English, and Dutch. The best results are produced by a model trained on clean modern data, including many  embeddings as input (FastText, character and multilingual Flair embeddings, BERT and historical embeddings computed with Flair on a historical corpus), and fine-tuned on a noisy historical groundtruth.

In conclusion, NER approaches based on deep learning seem to be more suitable for dealing with historical texts as they adapt more easily to OCR errors than rule-based approaches. Recent work in this area suggests that the impact of OCR quality on NER can be reduced by using different strategies. On the one hand, if the OCR error rate is kept below a certain threshold, the NER models remain little impacted: it is therefore important to reduce OCR errors as much as possible, but a low error rate may remain acceptable. On the other hand, it seems beneficial to reuse a NER model trained on modern data and adapt it to historical texts using supervised or unsupervised approaches.
